Contextuality and Nonlocality in Discrete Quantum Theory

### 2015-11-29 DQC3.tex
Keep updating comments on "The Concept of Contextuality and its..."

In order to prove by contradiction, assume the quantum physics is
non-contextuality, i.e., 
\begin{enumerate}
\item \label{enu:non-contextuality}Given an observable $\mathbf{O}$, the
predetermined definite outcome $v\left(\mathbf{O}\right)$ does not
depend on the choice of compatible observables that may be preformed
together with it. (postulate I in page 207 in \cite{peres1995quantum}).
\end{enumerate}
This leads to the premise of the Kochen-Specker theorem
\begin{enumerate}[resume]
\item \label{enu:premise}For a set of commuting projection operator $\proj{n}$,
if $\left\{ \ket{n}\right\} $ forms a basis, then $\sum_{n}v\left(\proj{n}\right)=1$.
(page 196 in \cite{peres1995quantum}).
\end{enumerate}
The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
to be satisfied so that postulate (\ref{enu:non-contextuality}) fails,
and the quantum theory is contextual .

Schumacher and Westmoreland~\cite{2010arXiv1010.5452S} uses Premise
(\ref{enu:premise}) instead of Postulate (\ref{enu:non-contextuality})
as the definition of non-contextuality because lack of commuting observables
in their theory. Our paper can do better and use Assumption (\ref{enu:non-contextuality})
as non-contextuality.

>>>>

In order to prove by contradiction, assume the quantum physics is
non-contextuality, i.e., 
\begin{enumerate}
\item \label{enu:non-contextuality}Given an observable $\mathbf{O}$, we
can predetermine a definite measurement outcome $v\left(\mathbf{O}\right)$
not depending on the choice of compatible observables that may be
preformed together with it. (postulate I in page 207 in \cite{peres1995quantum}).
\end{enumerate}
This leads to the premise of the Kochen-Specker theorem
\begin{enumerate}[resume]
\item \label{enu:premise}We can also define $v$ on states by $v\left(\ket{n}\right)=v\left(\proj{n}\right)$.
If $\left\{ \ket{n}\right\} $ forms a orthonormal basis, then $\sum_{n}v\left(\ket{n}\right)=1$.
(page 196 in \cite{peres1995quantum}).
\end{enumerate}
The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
to be satisfied so that Postulate (\ref{enu:non-contextuality}) fails,
and the quantum theory is contextual .

Because lack of commuting observables in their theory, Schumacher
and Westmoreland~\cite{2010arXiv1010.5452S} uses ``$v$ is well-defined
on states'' instead of Postulate (\ref{enu:non-contextuality}) as
the definition of non-contextuality. However, comparing to Postulate
(\ref{enu:non-contextuality}), it is less clear why ``$v$ is well-defined
on states'' should be a postulate or not.
